Homework 1 - Stat 495

### 2022-09-14 homework/hmk1/hmk1Stat495F22.Rmd
Working on Hw1

---
title: "Homework 1 - Stat 495"
author: "YourNameGoesHere"
date: "Due Monday, Sept. 12th by midnight"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
library(broom)
options(digits = 6)
```

@@

```{r}
# Hint, augment is likely to be useful here (loaded in broom package above)
# Do you remember how to add powers to a regression? You can also use mutate. 
# Be sure you actually get a cubic regression! 
# The model must show the appropriate terms.
```

@@

@@

@@

@@

@@

@@

>>>>

---
title: "Homework 1 - Stat 495"
author: "Justin Papagelis"
date: "Due Monday, Sept. 12th by midnight"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
library(broom)
library(tidyverse)
library(ggplot2)

options(digits = 6)
```

@@

```{r}
# Hint, augment is likely to be useful here (loaded in broom package above)
lm2 = lm(tot ~ poly(age, degree = 3), data = kidney)

ggplot(data = kidney, aes(x = age, y = tot)) +
  geom_point()

msummary(lm2)

ages = data.frame(age = c(20, 30, 40, 50, 60, 70, 80))

pred = augment(x = lm2, data = kidney, newdata = ages, se_fit = TRUE) %>%
  rename("Age" = age, "Estimation" = .fitted, "Standard Errors"= .se.fit)

pred %>% knitr::kable(bookends = TRUE)
# Do you remember how to add powers to a regression? You can also use mutate. 
# Be sure you actually get a cubic regression! 
# The model must show the appropriate terms.
```

@@

SOLUTION: Compared to the results in Table 1.1, the estimates using the cubic model are similar to the ones in Table 1.1. It does seem that the estimates tend to be lower than the other estimates for smaller ages using the cubic model. But as the ages increase, the estimated overall function of the kidneys is closer to the estimates of the first model. In general, the standard errors of the cubic model are higher than the standard errors of the estimates using the previous model.

@@

SOLUTION: The mean of the ALL group for the gene 136 is 0.752 and the mean of the AML group for the gene 136 is 0.950.

@@

```{r}
leukemia_ALL <- leukemia %>%
  filter(type == "ALL")

# resample(filter(leukemia, type == "ALL"))

set.seed = 0
results_ALL <- do(1000)*mean(~gene136, data = mosaic::resample(leukemia_ALL, replace = T))

ggplot(data = results_ALL, aes(x = mean)) +
  geom_density()

```

SOLUTION: The distribution of the means is unimodal and symmetric while centered around 0.76. The distribution appears to be relatively Normal.

@@

```{r}
leukemia_AML <- leukemia %>%
  filter(type == "AML")

set.seed = 0
results_AML <- do(1000)*mean(~gene136, data = mosaic::resample(leukemia_AML, replace = T))

ggplot(data = results_AML, aes(x = mean)) +
  geom_density()
```

SOLUTION: The distribution of the means of AML is unimodal and relatively symmetric. The distribution is centered around approximately 0.95.

@@

```{r}
results_ALL <- results_ALL %>%
  mutate(type = "ALL")

results_AML <- results_AML %>%
  mutate(type = "AML")

results_both <- rbind(results_ALL, results_AML)

ggplot(data = results_both, aes(x = mean, color = type)) +
  geom_density()
```

SOLUTION: From the density plots above, it appears that there is a difference in means for the ALL and the AML groups for gene 136. Specifically, a hypothesis could be that the mean of the AML group is greater than the mean of the ALL group for gene 136.

@@

SOLUTION: some sort of randomization procedure that compares the two groups directly

2-sample permuation test --> describe it good.
